---
title: "African American Authors"
author: "Daniel Sineus"
date: "11/11/2019"
output: word_document
---

**SENTIMENT ANALYSIS TO STUDY SOME BLACK AFRICAN AMERICAN LEADERS**

**Objective**: *the primary aim of this paper is to present a correlation of the different* texts and the authors advocating the same cause. 

*These authors are the following:*

* W.E.B DUBOIS
* FREDERICK DOUGLAS
* ZORA NEALE HURSTON

# The setting for the analysis
The gutenbergr will be used to find the ID. Different ways of proceeding will be presented

```{r setu, include=TRUE, echo=TRUE}
library(gutenbergr) # We are supposed it was already installed
library(dplyr)
gutenberg_metadata%>%
  filter(title=="The Marrow of Tradition") 

```
It was just an example in case you know the title of book. But this is not the case

Let's begin by looking for the ID of Douglas's books and download the books by ID

```{r seup, include=TRUE, echo=TRUE}
gutenberg_works(author=="Douglass, Frederick")
fred_books<-gutenberg_download(c(23,99,202,31839,34915), meta_fields = "title")
```
let's do the same for Booker T. Washington
```{r se, include=TRUE, echo=TRUE}
gutenberg_works(author=="Washington, Booker T.")
booker_books<-gutenberg_download(c(2376,26507,45125), meta_fields = "title")
head(booker_books)
```

#Here comes the turn for Zora Neale Hurston
```{r srte, include=TRUE, echo=TRUE}
library(stringr)
gutenberg_works(str_detect(author, "Hurston, Zora Neale"))
neale_books<-gutenberg_download(c(15902,19435,17187,22146), meta_fields = "title")
```


```{r set, include=TRUE, echo=FALSE}
library(stringr)
dubois_books<-gutenberg_download(c(31254,15210,35399,15265,408), meta_fields = "title")
head(dubois_books)
```

Count numbers of words in each text or words per book 
For Dubois
```{r setup, include=TRUE, echo=TRUE}
library(knitr)
kable(dubois_books%>%
  count(title))
```
Count numbers of words in each text or words per book 
For Booker T. Washington
```{r ret, include=TRUE, echo=TRUE}
library(knitr)
kable(booker_books%>%
  count(title))
```
Count numbers of words in each text or words per book 
For Neale Hurston
```{r seti, include=TRUE, echo=TRUE}
library(knitr)
kable(neale_books%>%
  count(title))
```

Frequency for words for the books considered 
For Neale Hurston
```{r hurst, include=TRUE, echo=TRUE}
library(knitr)
library(tidytext)
str(neale_books)
book1<-neale_books%>%
  unnest_tokens(word, text)%>%
  anti_join(stop_words)
str(book1)
## Count words for Neale's books all together
n_book1<-book1%>%
  count(word,sort = TRUE)
kable(head(n_book1, 20))
```


```{r neal, include=TRUE, echo=TRUE}
library(knitr)
book3<-neale_books%>%
  unnest_tokens(word, text)%>%
  anti_join(stop_words)
str(book3)
## Count words for Neale's books all together
n_book<-book3%>%
  count(word,sort = TRUE)
head(n_book, 20)
```



```{r boook, include=FALSE, echo=TRUE}
str(booker_books)
book2<-booker_books%>%
  unnest_tokens(word, text)%>%
  anti_join(stop_words)
str(book2)
## Count words for Neale's books all together
bfd<-book2%>%
  count(word,sort = TRUE)
head(bfd, 20)
```



```{r dubois, include=FALSE, echo=TRUE}
book4<-dubois_books%>%
  unnest_tokens(word, text)%>%
  anti_join(stop_words)
str(book4)
web<-book4%>%
  count(word, sort = TRUE)
head(web,20)
book5<-fred_books%>%
  unnest_tokens(word,text)%>%
  anti_join(stop_words)
str(book5)
fd<-head(book5,20)
fred<-book5%>%
  count(word, sort=TRUE)
head(fred, 20)
```


```{r frequency, include=TRUE, echo=TRUE}
library(dplyr)
library(tidyverse)
library(tidyr)
freq<-bind_rows(mutate(bfd, author="Booker T. Washington"),
                mutate(fred, author="Frederick Douglass"),
                mutate(web, author="Du Bois"))%>%
  mutate(word=str_extract(word, "[a-z']+"))%>%
  count(author, word)%>%
  group_by(author)%>%
  mutate(proportion=n/sum(n))%>%
  select(-n)%>%
  spread(author, proportion)%>%
  gather(author, proportion, `Booker T. Washington`:`Du Bois`)
freq<-drop_na(freq)
kable(head(freq,10))
```


```{r plot, include=TRUE, echo=FALSE, fig.cap="Word FREQU"}
library(scales)
ggplot(freq, aes(x=proportion, y="Frederick Douglass", color=abs(`Frederick Douglass`-proportion)))+
  geom_abline(color="gray40", lty=2)+
  geom_jitter(alpha=0.1, size=2.5, width = 0.3, height = 0.3) +
  geom_text(aes(label=word), check_overlap = TRUE, vjust=1.5)+
  scale_color_gradient(limits=c(0, 0.001), low="darkslategray4", high="gray75")+
  facet_wrap(~author, ncol = 2)+
  theme(legend.position = "none")+
  labs(y="Du Bois", x=NULL)
```

# Sentiment Analysis for Booker T. Washington and W.E.B DUBOIS
```{r sentiment, include=TRUE, echo=TRUE}
library(dplyr)
library(stringr)
library(tidytext)
booker_books<-gutenberg_download(c(2376,26507,45125), meta_fields = "title")
head(booker_books)
tidy_book<-booker_books%>%
  group_by(title)%>%
  mutate(linenumber=row_number(),
         chapter=cumsum(str_detect(text, regex("^chapter [\\divxlc]",                                               ignore_case = TRUE))))%>%
  ungroup()%>%
  unnest_tokens(word,text)
head(tidy_book,40)
library(tidytext)
library(textdata)
lexicon_nrc()
get_sentiments("afinn")
get_sentiments("nrc")
get_sentiments("bing")
nrc_joy<-get_sentiments("nrc")%>%
  filter(sentiment=="joy")
nrc_joy
rec<-tidy_book%>%
  filter(title=="Up from Slavery: An Autobiography")%>%
  inner_join(nrc_joy)%>%
  count(word, sort = TRUE)
head(rec)
nrc_sad<-get_sentiments("nrc")%>%
  filter(sentiment=="sadness")
nrc_sad
sad<-tidy_book%>%
  filter(title=="Up from Slavery: An Autobiography")%>%
  inner_join(nrc_sad)%>%
  count(word, sort = TRUE)
head(sad)
#Get sentiment for Booker T. Washington
rec1<-tidy_book%>%
  filter(title=="The Future of the American Negro")%>%
  inner_join(nrc_joy)%>%
  count(word, sort=TRUE)
head(rec1) # At that time, while was a symbol of priviledge compared to black people
rec2<-tidy_book%>%
  filter(title=="The Future of the American Negro")%>%
  inner_join(nrc_sad)%>%
  count(word, sort=TRUE)
head(rec2,10)
 rec3<-tidy_book%>%
   filter(title=="The Story of Slavery")%>%
   inner_join(nrc_joy)%>%
   count(word, sort = TRUE)
head(rec3)
rec4<-tidy_book%>%
   filter(title=="The Story of Slavery")%>%
   inner_join(nrc_sad)%>%
   count(word, sort = TRUE)
head(rec4)
# frequency and total of words per book
book2<-booker_books%>%
  group_by(title)%>%
  unnest_tokens(word, text)%>%
  anti_join(stop_words)%>%
  count(word, sort = TRUE)
head(book2)
  
total_book2<-book2%>%
  group_by(title)%>%
  summarise(total=sum(n))
head(total_book2)
book_words<-left_join(book2, total_book2)
ter<-book_words%>%
  mutate(tot=(n/total)*100)
head(ter)
ter1<-ter%>%
  filter(title=="The Future of the American Negro"& n>50)

#Sentiments for Booker T. Washington
dubois<-dubois_books%>%
  group_by(title)%>%
  mutate(linenumber=row_number(),
         chapter=cumsum(str_detect(text, regex("^chapter [\\divxlc]",                                               ignore_case = TRUE))))%>%
  ungroup()%>%
  unnest_tokens(word,text)
tail(dubois)
rec5<-dubois%>%
  filter(title=="The Souls of Black Folk")%>%
  inner_join(nrc_joy)%>%
  count(word, sort = TRUE)
head(rec5,10)
rec5_1<-dubois%>%
  filter(title=="The Souls of Black Folk")%>%
  inner_join(nrc_sad)%>%
  count(word, sort = TRUE)
head(rec5_1)
rec6<-dubois%>%
  filter(title=="The Negro in the South\nHis Economic Progress in Relation to his Moral and Religious Development")%>%
  inner_join(nrc_joy)%>%
  count(word, sort = TRUE)
head(rec6,10)
rec6_1<-rec5<-dubois%>%
  filter(title=="The Negro in the South\nHis Economic Progress in Relation to his Moral and Religious Development")%>%
  inner_join(nrc_sad)%>%
  count(word, sort = TRUE)
head(rec6_1)
rec7_1<-rec5<-dubois%>%
  filter(title=="The Quest of the Silver Fleece: A Novel")%>%
  inner_join(nrc_sad)%>%
  count(word, sort = TRUE)
head(rec7_1)
rec7<-ec6_1<-rec5<-dubois%>%
  filter(title=="The Quest of the Silver Fleece: A Novel")%>%
  inner_join(nrc_joy)%>%
  count(word, sort = TRUE)
head(rec7)
neale_tidy<-neale_books%>%
  group_by(title)%>%
  mutate(linenumber=row_number(),
         chapter=cumsum(str_detect(text, regex("^chapter [\\divxlc]",ignore_case = TRUE))))%>%
  ungroup()%>%
  unnest_tokens(word, text)
head(neale_tidy)
bing_word<-neale_tidy%>%
  inner_join(get_sentiments("bing"))%>%
  count(word, sentiment,sort = TRUE)%>%
  ungroup()
head(bing_word)
bing_word%>%
  group_by(sentiment)%>%
  top_n(30)%>%
  ungroup()%>%
  mutate(word=reorder(word, n))%>%
  ggplot(aes(word, n, fill=sentiment))+
  geom_col(show.legend = FALSE)+
  facet_wrap(~sentiment, scales = "free_y")+
  labs(y="Contribution to sentiment", x=NULL)+
  coord_flip()
```

```{r sent, include=TRUE, echo=TRUE}
#get Sentiments for Frederick Douglass
dubois_sentiment<-dubois%>%
  inner_join(get_sentiments("bing"))%>%
  count(title, index=linenumber%/%80, sentiment)%>%
  spread(sentiment, n, fill = 0)%>%
  mutate(sentiment=positive-negative)
dubois_sentiment
library(ggplot2)
ggplot(dubois_sentiment, aes(index, sentiment, fill=title))+
  geom_col(show.legend = FALSE)+
  facet_wrap(~title, ncol=2, scales = "free_x")
Booker_sentiment<-tidy_book%>%
  inner_join(get_sentiments("nrc"))%>%
  count(title, index=linenumber%/%80, sentiment)%>%
  spread(sentiment, n, fill = 0)%>%
  mutate(sentiment=joy-sadness)%>%
  select(title,index, sentiment)
head(Booker_sentiment)
ggplot(Booker_sentiment, aes(index, sentiment, fill=title))+
  geom_col(show.legend = FALSE)+
  facet_wrap(~title, ncol = 2, scales = "free_x")

booker_n<-tidy_book%>%
  inner_join(get_sentiments("bing"))%>%
  count(title, index=linenumber%/%80, sentiment)%>%
  spread(sentiment, n, fill = 0)%>%
  mutate(sentiment=positive-negative)
ggplot(booker_n, aes(index, sentiment, fill=title))+
  geom_col(show.legend = FALSE)+
  facet_wrap(~title, ncol = 2, scales = "free_x")
```


# check the distribution for each novel
```{r distribution, include=TRUE, echo=TRUE}
book_words%>%
  ggplot(aes(n/total), fill=title)+
  geom_histogram(show.legend = FALSE)+
  xlim(NA, 0.0009)+
  facet_wrap(~title, ncol = 2, scales = "free_y")%>%
  na.omit()

```



```{r zipf, include=TRUE, echo=TRUE}


```